### 2018-10-17 Paper/revision/reviewer_replies.tex

In the borehole test case, the degree of the PCE was found to be 3 in the reduced space (4D)
and 5 in the full space (7D). In the case of semilinear elliptic PDE, the degree of the PCE was 
found to be 3 in the reduced space (5D) as well as the original space (10D). For the reaction
kinetics application, the degree of the PCE was found to be 3 in the reduced space (4D) and 
2 in the full space (19D).

The captions of Figures 3, 6, and 8 have been updated to include this information.

\item
\referee{
P25, Figure 7, it seems that the rank of the parameters and the difference of
$\mu_s$ doesn't change too much over iterations. Does it indicate the initial
parameter screening  (line 1-6 in Algorithm 1) is good enough for ranking the
parameters? Can the authors plot the similar figure for other examples to see
if the iterative screening procedure does make a difference on the ranking the
parameters compared with the initial parameter screening step?}

The reviewer is correct in pointing out from Figure 7 that the initial screening step
reasonably approximates the screening metric. The same is observed in
Figure 5 for the semilinear elliptic PDE test case. It is also true in the borehole test
case and a similar figure has been included for this example in the revised manuscript
(Figure 2c) as suggested by the reviewer. The reason for this observation has already
been discussed in response to Comment~1 above and included in the revised manuscript.

@@

The above points are already included in the paragraph on the discussion of the proposed
methodology in Section 3. Nevertheless, based on the reviewer's feedback, we have tried to
clarify and emphasize these points in the first paragraph in Section 6 (Summary and Conclusion)
in the revised manuscript.

\item
\referee{The reviewer would also like to see the comparison of the computational cost
(not just the numerical results) of DGSMs to variance based sensitivity indices
with increasing parameter dimension, e.g. Sobol’ indices incorporated with
sparse grid, since the difference decreases with increasing number of parameters.}

\item 
\referee{In section 4 and 5, no predictive convergence using the test data sample is
presented, only the convergence of $\epsilon_\text{LOO}$, which reuses the training data as
the validation set, is shown. This shows only the convergence of the model,
and does not necessarily indicate the (predictive) accuracy of the constructed
model, hence could lead to false conclusion. The reviewer would like to see the
convergence of $\epsilon_{L_2}$.}

As suggested by the reviewer, the plots and related discussion pertaining to the convergence 
of $\epsilon_{L_2}$ have been included for the numerical tests presented in Section 3 (Figures 3b
and 6b) and 
the chemical kinetics application presented in Section 4 (Figure 8, right).

### 2018-10-24 Paper/revision/reviewer_replies.tex

Convergence behavior in this case depends upon the variability in the gradient of
$G(\theta)$ with respect to individual parameters, $\theta_i$ in their respective
domains. For the numerical tests and the application considered in this work, the
gradient is not observed to vary significantly in the considered domain of the
parameters. In other words, the variance of the estimator is low. 
Hence, a small number of Monte Carlo samples are able to estimate
the screening parameters. This is a common observation in many practical
applications, and therefore the proposed methodology involving an iterative
approach can yield significant computational savings.

These points have been emphasized in the discussion in Section~6 (Summary and
Conclusion) in the revised manuscript.

\item 
\referee{P17, Figure 3, what's the degree of the PCE used in the example? The same
question applies to Figure 6 and Figure 8.}

Sparse PCEs were constructed using least angle regression by means of UQLab software
for the two numerical tests (Borehole and the semilinear elliptic PDE),
and the reaction kinetics application in this work.  
In the borehole test case, the PCE constructed using 50 training points for the 7D, 5D, and
4D cases was found to be of degree 2, 2, and 3 respectively.  
In the semilinear elliptic PDE example, the PCE constructed using 90 training
points for the 10D and 5D cases was found to be of degree 2 and 3 respectively.
For the reaction kinetics application, the PCE constructed using 60 training points
for the 19D and 4D cases was found to be of degree 1 and 3 respectively.

### 2018-10-24 Paper/app.tex
..

The proposed framework in section~\ref{sec:method} is implemented to 
the H$_2$/O$_2$ reaction mechanism provided in~\cite{Yetter:1991}.
The H$_2$/O$_2$ reaction is gaining a lot of attention as a potential
source of clean energy for applications such as 
transportation~\cite{Das:1996}. 
The mechanism comprises of 19 reactions including chain reactions,
dissociation/recombination reactions, and formation and consumption
of intermediate species as provided below in Table~\ref{tab:kinetics}.

@@

We apply the parameter screening algorithm with the following
parameters: $\tau_\text{screen}$, $s_\text{min}$,
$s_\text{max}$, $\beta$ are fixed at 0.2, 3, 10, and 1.0 respectively for both cases.
Additionally, the value of $\tau$ is considered to be 1.0$\times 10^{-17}$ and
5.0$\times 10^{-17}$ in the rich and lean case respectively. Such a small value
of $\tau$ for this application is a consequence of the nature of convergence exhibited
by the sensitivity measures. Moreover, the screening procedure is carried out
for atleast $s_\text{min}$ number of iterations in order to bolster our confidence
in the estimates.

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_kinetics_rich}
  \includegraphics[width=0.48\textwidth]{./Figures/ub_conv_kinetics_lean}
  \\ \vspace{2mm}
  \includegraphics[width=0.48\textwidth]{./Figures/mu_rich}
  \includegraphics[width=0.48\textwidth]{./Figures/mu_lean}
\caption{Top: Estimates of $\widehat{\mathcal{C}_i\mu_i}$ for $A_i$'s in the case
of fuel-rich mixture~(left) and fuel-lean mixture~(right). Bottom: The value of
$\Delta\mu_s$ during three iterations within the screening step are plotted for
the case of fuel-rich mixture~(left) and fuel-lean mixture~(right).}
\label{fig:sense_kinetics}
\end{center}
\end{figure}
%
The screening metric estimates in the above plots are observed to converge with
only a few samples (5--10). Moreover, out of the 19 uncertain pre-exponents,
only $A_1$, $A_9$, $A_{15}$, and $A_{17}$ seem to be important in the fuel-rich
case, whereas, only $A_1$, $A_9$, and $A_{15}$ seem important in the fuel-lean
case, based on the value of $\tau_\text{screen}$. These observations are indicative
of the potential for significant reduction in the dimensionality of this problem. 
A reduced-space
surrogate constructed using the proposed framework could thus lead to large computational
gains. The decay of $\Delta\mu_s$ with iterations is expected and builds our confidence
in the screening procedure in both cases.

A reduced-space surrogate (RSS) was constructed in 4D for the fuel-rich case,
and in 3D for
the fuel-lean case. Figure~\ref{fig:err_samples_kinetics}~(left) illustrates a
comparison of convergence characteristics for the PCEs constructed in the
full-space and the reduced-space for the fuel-rich case. Note that the
plot is generated using the implementation of least angle regression (LAR)
for sparse PCEs in UQLab.  
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_kinetics}
   \includegraphics[width=0.44\textwidth]{./Figures/errL2_samples_kinetics}
\caption{Left: A semi-log plot of $\epsilon_\text{\tiny LOO}$ as a function of
number of model evaluations in the full-space (19D) and the reduced-space (4D)
for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. \rebut{The degree of
the resulting PCE was found to be 3 and 2 in the 4D and the 19D case respectively.
Right: Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$)
for the PCEs constructed in 4D and 19D.}}
\label{fig:err_samples_kinetics}
\end{center}
\end{figure}
%
The leave-one-out cross validation error is observed to drop initially
and plateau with the increase in training points for the 19-dimensional
PCE. However, in the case of 4-dimensional PCE, the error exhibits a
monotonic behavior and is found to be smaller than $\mathcal{O}(10^{-5})$
at 60 training points. Clearly, the RSS shows a much faster rate of convergence.
\rebut{Additionally, the
convergence of the relative error norm, $\epsilon_{\mbox{\tiny{L-2}}}$ in 
Figure~\ref{fig:err_samples_kinetics}~(right) indicates that for the case of 10
samples, the 4D PCE is observed to be more accurate. However, the 19D PCE
is observed to be more accurate by an order of magnitude as the sample size
increases. Specifically, the 4D PCE was found to be accurate within 1.8$\%$ in the
fuel-rich case, and within 3.1$\%$ in the fuel-lean case. Therefore, the 4D PCE
is still observed to be reasonably accurate in this case. Moreover, its faster convergence
as mentioned earlier should help reduce computational effort associated with
surrogate model construction.}
Similar trends (not included) were observed in the fuel-lean case.

Model evaluations at 1000 samples in the test suite
are further used to plot a normalized histogram of the ignition time in 
Figure~\ref{fig:pdf_kinetics}. To verify the accuracy of the RSS in a 
probabilistic-sense, we compare the histogram plot with a PDF of ignition time
using surrogate predictions at 10$^{6}$ samples in the reduced space in both cases. 
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_rich}
  \includegraphics[width=0.48\textwidth]{./Figures/pdf_comp_lean}
\caption{A normalized histogram based on model evaluations at 1000 samples is plotted
along with a PDF of ignition delay for the fuel-rich case (left) and the fuel-lean
case (right).}
\label{fig:pdf_kinetics}
\end{center}
\end{figure}
%
Clearly, the RSS captures the spread as well as the modal estimate of
the ignition delay in both scenarios. Hence, the proposed framework 
has enabled significant dimension reduction and construction of an accurate
RSS for multiple scenarios pertaining to the H$_2$/O$_2$ reaction
mechanism.

>>>>

The proposed framework in section~\ref{sec:method} is implemented to 
the H$_2$/O$_2$ reaction mechanism provided in~\cite{Yetter:1991}.
The H$_2$/O$_2$ reaction is gaining a lot of attention as a potential
source of clean energy for applications such as 
transportation~\cite{Das:1996} and fuel cell 
applications~\cite{Loges:2008,Cosnier:2016}. \rebut{We begin by providing
the necessary background information for setting up the problem
in~\ref{sub:setup}. Results and discussion based on the implementation
of the proposed framework are provided in~\ref{sub:imp}. Finally, 
in~\ref{sub:cost}, we
provide a comparative analysis of the computational cost involved
in determining relative parameter importance using DGSMs and the
total-effect Sobol index as the dimensionality increases from 19 to 33
for the present application.}

\subsection{Problem Set-up}
\label{sub:setup}  
The mechanism comprises of 19 reactions including chain reactions,
dissociation/recombination reactions, and formation and consumption
of intermediate species as provided below in Table~\ref{tab:kinetics}.

@@

\subsection{DGSM-guided surrogate construction}
\label{sub:imp}
We apply the parameter screening algorithm with the following
parameters: $\tau_\text{screen}$, $s_\text{min}$,
$s_\text{max}$, $\beta$ are fixed at 0.2, 3, 10, and 1.0 respectively for both cases.
Additionally, the value of $\tau$ is considered to be 1.0$\times 10^{-17}$ and
5.0$\times 10^{-17}$ in the rich and lean case respectively. Such a small value
of $\tau$ for this application is a consequence of the nature of convergence exhibited
by the sensitivity measures. Moreover, the screening procedure is carried out
for atleast $s_\text{min}$ number of iterations in order to bolster our confidence
in the estimates.

@@

\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_kinetics_rich}
  \includegraphics[width=0.45\textwidth]{./Figures/ub_conv_kinetics_lean}
  \\ \vspace{2mm}
  \includegraphics[width=0.45\textwidth]{./Figures/mu_rich}
  \includegraphics[width=0.45\textwidth]{./Figures/mu_lean}
\caption{Top: Estimates of $\widehat{\mathcal{C}_i\mu_i}$ for $A_i$'s in the case
of fuel-rich mixture~(left) and fuel-lean mixture~(right). Bottom: The value of
$\Delta\mu_s$ during three iterations within the screening step are plotted for
the case of fuel-rich mixture~(left) and fuel-lean mixture~(right).}
\label{fig:sense_kinetics}
\end{center}
\end{figure}
%
The screening metric estimates in the above plots are observed to converge with
only a few samples (5--10). Moreover, out of the 19 uncertain pre-exponents,
only $A_1$, $A_9$, $A_{15}$, and $A_{17}$ seem to be important in the fuel-rich
case, whereas, only $A_1$, $A_9$, and $A_{15}$ seem important in the fuel-lean
case, based on the value of $\tau_\text{screen}$. These observations are indicative
of the potential for significant reduction in the dimensionality of this problem. 
A reduced-space
surrogate constructed using the proposed framework could thus lead to large computational
gains. The decay of $\Delta\mu_s$ with iterations is expected and builds our confidence
in the screening procedure in both cases.

A reduced-space surrogate (RSS) was constructed in 4D for the fuel-rich case,
and in 3D for
the fuel-lean case. Figure~\ref{fig:err_samples_kinetics}~(left) illustrates a
comparison of convergence characteristics for the PCEs constructed in the
full-space and the reduced-space for the fuel-rich case. Note that the
plot is generated using the implementation of least angle regression (LAR)
for sparse PCEs in UQLab.  
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_kinetics}
   \includegraphics[width=0.44\textwidth]{./Figures/errL2_samples_kinetics}
\caption{Left: A semi-log plot of $\epsilon_\text{\tiny LOO}$ as a function of
number of model evaluations in the full-space (19D) and the reduced-space (4D)
for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. \rebut{The degree of
the PCE constructed using 60 training points was found to be 1 and 3 in the 19D and the 4D cases respectively.
Right: Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$)
for the PCEs constructed in 4D and 19D.}}
\label{fig:err_samples_kinetics}
\end{center}
\end{figure}
%
The leave-one-out cross validation error is observed to drop initially
and plateau with the increase in training points for the 19-dimensional
PCE. However, in the case of 4-dimensional PCE, the error exhibits a
monotonic behavior and is found to be smaller than $\mathcal{O}(10^{-5})$
at 60 training points. Clearly, the RSS shows a much faster rate of convergence.
\rebut{Additionally, the
convergence of the relative error norm, $\epsilon_{\mbox{\tiny{L-2}}}$ in 
Figure~\ref{fig:err_samples_kinetics}~(right) indicates that for the case of 10
samples, the 4D PCE is observed to be more accurate. However, the 19D PCE
is observed to be more accurate by an order of magnitude as the sample size
increases. Specifically, the 4D PCE was found to be accurate within 1.8$\%$ in the
fuel-rich case, and within 3.1$\%$ in the fuel-lean case. Therefore, the 4D PCE
is still observed to be reasonably accurate in this case. Moreover, its faster convergence
as mentioned earlier should help reduce computational effort associated with
surrogate model construction.}
Similar trends (not included) were observed in the fuel-lean case.

Model evaluations at 1000 samples in the test suite
are further used to plot a normalized histogram of the ignition time in 
Figure~\ref{fig:pdf_kinetics}. To verify the accuracy of the RSS in a 
probabilistic-sense, we compare the histogram plot with a PDF of ignition time
using surrogate predictions at 10$^{6}$ samples in the reduced space in both cases. 
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_rich}
  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_lean}
\caption{A normalized histogram based on model evaluations at 1000 samples is plotted
along with a PDF of ignition delay for the fuel-rich case (left) and the fuel-lean
case (right).}
\label{fig:pdf_kinetics}
\end{center}
\end{figure}
%
Clearly, the RSS captures the spread as well as the modal estimate of
the ignition delay in both scenarios. Hence, the proposed framework 
has enabled significant dimension reduction and construction of an accurate
RSS for multiple scenarios pertaining to the H$_2$/O$_2$ reaction
mechanism.

\rebut{
\subsection{Comparative cost analysis}
\label{sub:cost}

In this section, we perform a comparative analysis of the computational cost
associated with obtaining converged estimates of parametric sensitivities
using DGSM, and the total-effect Sobol indices ($\mathcal{T}(\theta_i)$). The former is computed
using the parameter screening algorithm (Algorithm~\ref{alg:screen}), and the latter is
estimated analytically using a sparse-basis PCE. Note that estimating $\mathcal{T}(\theta_i)$
using a PCE has been shown to be more efficient compared to sampling techniques.
Moreover, a sparse-basis PCE is expected to require fewer training points which
enhances computational savings. To investigate the impact of the dimensionality, the
analysis is performed with 19 uncertain parameters, i.e.
the pre-exponents~($A_i$'s) as discussed earlier in~\ref{sub:setup} and~\ref{sub:imp}, and
33 uncertain parameters wherein the activation energies~($E_{a,i}$'s) are also considered to
be uncertain. The $E_{a,i}$'s are also considered to be uniformly distributed in the
interval: [$0.9E_{a,i}^\ast,1.1E_{a,i}^\ast$], where $E_{a,i}^\ast$ is the nominal value
for the $i^\text{th}$ reaction as provided in~\cite{Yetter:1991}. Note that only those
$E_{a,i}$'s with a non-zero nominal value are considered as uncertain, and therfore the
total number of uncertain parameters in the high-dimensional case is 33 as opposed to 38.

The 33-dimensional sparse basis PCE was assessed for its convergence characteristics
and its predictive accuracy using $\epsilon_{\mbox{\tiny LOO}}$~(see~\eqref{eq:loo}) and
$\epsilon_{\mbox{\tiny{L-2}}}$~(see~\eqref{eq:l2}) respectively as shown in
Figure~\ref{fig:err_samples}.  
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_kinetics33D}
\caption{A semi-log plot of $\epsilon_\text{\tiny LOO}$  and $\epsilon_{\mbox{\tiny{L-2}}}$
as a function of the number of training points in the 33D parameter space 
for the fuel (H$_2$)-rich case i.e. $\phi$ = 2.0. The degree of
the PCE constructed using 500 training points was found to be 3.}
\label{fig:err_samples}
\end{center}
\end{figure}
%
The sparse-basis PCEs constructed in the 19 and the 33 dimensional parameter
space are considered to have converged once $\epsilon_\text{\tiny LOO}$ is found to be
smaller than 6.0$\times$10$^{-3}$. As observed in Figures~\ref{fig:err_samples_kinetics}
and~\ref{fig:err_samples}, the number of training points required in the 19D
and the 33D cases are found to be 60 and 500 respectively. As expected, the predictive
accuracy is observed to increase with increase in the number of training points in both cases.
The estimate of $\epsilon_{\mbox{\tiny{L-2}}}$ was found to be 7.22$\times$10$^{-2}$ using the
converged 33D PCE and an independent set of model evaluations at 1000 samples.

Sensitivity estimates for the 33 uncertain parameters are hence determined
using the DGSM-based strategy and by evaluating $\mathcal{T}(\theta_i)$ analytically
using the sparse-basis PCE as discussed earlier in this section. The estimates based
on the two approaches were plotted separately and placed side-by-side for comparison
in Figure~\ref{fig:sense33D}.
%
\begin{figure}[htbp]
 \begin{center}
  \includegraphics[width=0.42\textwidth]{./Figures/ub33D}
  \includegraphics[width=0.40\textwidth]{./Figures/sens_kinetics33D}
\caption{
Left: Estimates of the screening metric ($\widehat{\mathcal{C}_i\mu_i}$) for each 
uncertain parameter, obtained using $N$ = 5, 10, 15, and 20 samples in the full parameter space.
Right: Sobol' total sensitivity index, $\mathcal{T}(\theta_i)$ for uncertain parameters in the
semilinear elliptic PDE~\eqref{eq:semilinear}.}
\label{fig:sense33D}
\end{center}
\end{figure}
%

}

### 2018-10-24 Paper/examples.tex
..

\begin{figure}[htbp]
 \begin{center}
 \begin{tabular}{cc}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_borehole}
  &
  \includegraphics[width=0.45\textwidth]{./Figures/errL2_samples_borehole}
  \\ (a) & (b)
  \end{tabular}
  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_borehole}
  \\ (c)
\caption{(a) A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions. \rebut{The degree of
the resulting PCE was found to be 3, 2,and 5 in the 4D, 5D, and 7D case respectively;
(b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 
for the PCEs constructed in 4D, 5D, and 7D};
and (c) A comparison of
PDFs of the discharge, $\mathcal{Q}$, generated using 10$^{6}$ samples from
the marginal distributions of the uncertain parameters in each case.} 
\label{fig:conv_bore}
\end{center}
\end{figure}
%
As expected, it is observed that the PCE constructed in the 4D space converges
at a much faster rate. For instance, if a PCE with $\mathcal{O}(10^{-4})$
accuracy is sought, we need function evaluations at only about 50 sample points
in the 4D parameter space whereas the number of samples needed in the full 7D
space seems much higher. Latin hypercube sampling (LHS) was used in
each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}(a)
is not expected to decrease monotonically with the increase in sample size
owing to the penalty term in the regularized optimization problem in Eq.~\ref{eq:reg}. 
\rebut{However, the plot of $\epsilon_{\mbox{\tiny{L-2}}}$ as a function of sample
size for the three surrogate models in Figure~\ref{fig:conv_bore}(b)
clearly demonstrates the trade-off between
computational effort associated with surrogate construction and its predictive 
accuracy. For a small sample size of 20, the relative  error in the case of 4D
PCE is found to be the smallest. However, as the sample size increases, the higher
order PCE becomes more accurate. Note that the same set of 50 samples in the
validation test suite were used in each case. Hence, when limited computational resources
are available, the proposed methodology could yield substantial gains due to fast
convergence as well as higher accuracy of the surrogate in the reduced space.
The gains are expected to increase exponentially as the dimensionality of the 
input space increases.}

@@

the resulting PCE was found to be 3 in both cases; 

>>>>

\begin{figure}[htbp]
 \begin{center}
 \begin{tabular}{cc}
  \includegraphics[width=0.45\textwidth]{./Figures/err_samples_borehole}
  &
  \includegraphics[width=0.45\textwidth]{./Figures/errL2_samples_borehole}
  \\ (a) & (b)
  \end{tabular}
  \includegraphics[width=0.45\textwidth]{./Figures/pdf_comp_borehole}
  \\ (c)
\caption{(a) A comparison of order of the leave-one-out-error 
($\epsilon_{\mbox{\tiny{LOO}}}$) as a function of number of regression samples
used for constructing the PCE in 4, 5, and 7 dimensions. \rebut{The degree of
the PCE using 50 training points was found to be 3, 2,and 2 in the 4D, 5D, and 7D case respectively;
(b) Semilog plot of the relative L-2 error norm ($\epsilon_{\mbox{\tiny{L-2}}}$) 
for the PCEs constructed in 4D, 5D, and 7D};
and (c) A comparison of
PDFs of the discharge, $\mathcal{Q}$, generated using 10$^{6}$ samples from
the marginal distributions of the uncertain parameters in each case.} 
\label{fig:conv_bore}
\end{center}
\end{figure}
%
As expected, it is observed that the PCE constructed in the 4D space converges
at a much faster rate. For instance, if a PCE with $\mathcal{O}(10^{-4})$
accuracy is sought, we need function evaluations at only about 50 sample points
in the 4D parameter space whereas the number of samples needed in the full 7D
space seems much higher. Latin hypercube sampling (LHS) was used in
each case. It must be pointed out that the error in Figure~\ref{fig:conv_bore}(a)
is not expected to decrease monotonically with the increase in sample size
owing to the penalty term in the regularized optimization problem in Eq.~\ref{eq:reg}. 
\rebut{However, the plot of $\epsilon_{\mbox{\tiny{L-2}}}$ as a function of sample
size for the three surrogate models in Figure~\ref{fig:conv_bore}(b)
clearly demonstrates the trade-off between
computational effort associated with surrogate construction and its predictive 
accuracy. For a small sample size of 20, the relative  error in the case of 4D
PCE is found to be the smallest. However, as the sample size increases, the higher
order PCE becomes more accurate. Note that the same set of 50 samples in the
validation test suite were used in each case. Hence, when limited computational resources
are available, the proposed methodology could yield substantial gains due to fast
convergence as well as higher accuracy of the surrogate in the reduced space.
The gains are expected to increase exponentially as the dimensionality of the 
input space increases.}

@@

the PCE constructed using 90 training points was found to be 2 and 3 in the
10D and 5D cases respectively; 
